%% The MIT License (MIT)
%%
%% Copyright (c) 2015 Daniil Belyakov
%%
%% Permission is hereby granted, free of charge, to any person obtaining a copy
%% of this software and associated documentation files (the "Software"), to deal
%% in the Software without restriction, including without limitation the rights
%% to use, copy, modify, merge, publish, distribute, sublicense, and/or sell
%% copies of the Software, and to permit persons to whom the Software is
%% furnished to do so, subject to the following conditions:
%%
%% The above copyright notice and this permission notice shall be included in all
%% copies or substantial portions of the Software.
%%
%% THE SOFTWARE IS PROVIDED "AS IS", WITHOUT WARRANTY OF ANY KIND, EXPRESS OR
%% IMPLIED, INCLUDING BUT NOT LIMITED TO THE WARRANTIES OF MERCHANTABILITY,
%% FITNESS FOR A PARTICULAR PURPOSE AND NONINFRINGEMENT. IN NO EVENT SHALL THE
%% AUTHORS OR COPYRIGHT HOLDERS BE LIABLE FOR ANY CLAIM, DAMAGES OR OTHER
%% LIABILITY, WHETHER IN AN ACTION OF CONTRACT, TORT OR OTHERWISE, ARISING FROM,
%% OUT OF OR IN CONNECTION WITH THE SOFTWARE OR THE USE OR OTHER DEALINGS IN THE
%% SOFTWARE.

% The font could be set to Windows-specific Calibri by using the 'calibri' option

% !TeX program = lualatex

\documentclass[]{mcdowellcvcustom}

% For mathematical symbols
\usepackage{amsmath}


%for left center right alignment
\newcommand{\headerline}[3]{%
	\par\medskip\noindent
	\makebox[0pt][l]{\texttt{#1}}%
	\makebox[\textwidth][c]{#2}%
	\makebox[0pt][r]{\texttt{#3}}\par\medskip}

% Set applicant's personal data for header
\name{Nicholas Cochrane}
\address{3855 N Peach Ave \linebreak Fresno, California 93727}
\contacts{(559) 676-7957 \linebreak nicholascochrane.dev@gmail.com}

\begin{document}

	% Print the header
	\makeheader
	
	\headerline{linkedin.com/in/nicholas-cochrane-dev}{ }{github.com/Nicholas-Cochrane}
	
	% Print the content
	\begin{cvsection}{Summary}
		\begin{cvsubsection}{}{}{}
		I have over 2 years of casino surveillance tech experience and over 3 years of combined IT experience. Skilled in installing, configuring, and maintaining indoor and outdoor IP camera systems, ensuring reliable camera coverage for maintaining MICS compliance. Proficient in computer repair, IT troubleshooting, and Layer 3 VLAN/IP networking, with hands-on experience running and terminating Ethernet cabling and configuring switches. Recognized for strong problem-solving abilities, rapid emergency on-call response, and maintaining system uptime in critical situations.
		\end{cvsubsection}
	\end{cvsection}
	
	\vspace{6mm}
	
	\begin{cvsection}{Employment\slash Experience}
		\begin{cvsubsection}{High School IT Support}{Minarets High School}{August 2014 - June 2015}			
			\begin{itemize}
				\item Volunteered working for high schools IT support team. 
				\item Computer repair, Computer imaging, Tech support
			\end{itemize}
		\end{cvsubsection}
		\vspace{2mm}
		\begin{cvsubsection}{Computer Repair and Imaging}{Minarets High School}{Summer 2015}			
			\begin{itemize}
				\item Summer Job at Minarets High School repairing and re-imaging laptops for the next school year. Along with helping setting up new, and removing old student accounts.
			\end{itemize}
		\end{cvsubsection}
		\begin{cvsubsection}{Retail Sales Associate}{Best Buy}{September 2023 - January 2024}			
			\begin{itemize}
				\item Seasonal computer sales associate.
				\item Helping customers find the best computer, cables, computer part, or accessory for their situation or problem.
				\item Stocking, cleaning, and organizing store products.
			\end{itemize}
		\end{cvsubsection}
		\begin{cvsubsection}{Surveillance/IT Technician}{Picayune Rancheria of the Chukchansi Indians Tribal Gaming Commission}{Feb 2024 - Present}			
			\vspace{5mm}
			\begin{itemize}
				\item Maintaining and installing surveillance and  networking equipment to insure 24/7 operation and compliance with MICS regulations.
				\item Emergency on call response. Helped restore system after full system failure due to unplanned power outage causing equipment damage.
				\item Installing Pelco and Axis brand cameras; Cisco, Extreme, and NTV Phybridge networking equipment; and worked in and setting up Pelco VideoXpert, Avigilon Unity, and Mirasys VMSs.
				\item Running and Terminating Indoor/Outdoor network cabling.
				\item Installing and maintaining workstations, desktop computers, and printers across multiple networks.
				\item Working at height on ladders and aerial lift platforms. Operating Scissor and Boom lifts.
			\end{itemize}
		\end{cvsubsection}

	\end{cvsection}
	
	
	\begin{cvsection}{Education}
		\begin{cvsubsection}{Fresno, CA}{California State University, Fresno}{August 2015 -- May 2020}
			\begin{itemize}
				\item Graduated Spring 2020 
				\item B.S. in Computer Science. GPA: 3.90
				\item Undergraduate Coursework: Operating Systems; Databases; Big Data Analysis and Data Mining; Algorithms; Reinforcement Learning; Calculus II; Computer Graphics.
			\end{itemize}
		\end{cvsubsection}
	\end{cvsection}
	
	\pagebreak
	
	\begin{cvsection}{Technical Experience}
		\begin{cvsubsection}{Projects}{}{}
			\begin{itemize}
				\item \textbf{Home Server} (2023) An at home linux server running a jellyfin docker image, and a postgresDB and display of local in home air quality sensors. Bash script, Docker, SSH, SFTP, SSL, Nginx, Postgres, Grafana
				\item \textbf{Reversi Website} (2019). Working game site with login, online saving, reloading, AI opponents and high score Tracking.  HTML, CSS, JavaScript, jQuery, PHP, Ajax, SQL
				\item \textbf{Pattern Analysis for Transaction Fraud Detection} (2020). \textbf{DOI}: 10.1109/CCWC51732.2021.9376045 Data Analysis paper examining the patterns of transaction fraud in large data sets. Presented at IEEE CCWC 2021. \LaTeX, Python, Numpy, Pandas, Matplotlib
				\item \textbf{Chukchansi Analog to Digital Upgrade} (2024). Helped coordinate a Camera system upgrade switching older cameras and converting analog cameras to digital IP cameras. 
				\item \textbf{Mirasys and Unity Demos} (2025). Installed and set up full Avigilon Unity and Mirasys demos alongside existing VMS systems.
				
			\end{itemize}
		\end{cvsubsection}
	\end{cvsection}
	
	\vspace{10mm}

	\begin{cvsection}{Languages and Technologies}
		\begin{cvsubsection}{}{}{}	
			\begin{itemize}
				\item Linux; Bash script; VIM; SSH
				\item Windows (7,8,10,11); CMD; Powershell
				\item HTML; CSS; JavaScript; JSON; PHP; Ajax; Nginx, SSL
				\item SQL (mySQL,Postgres); Hadoop; Spark; Docker; Grafana; Excel
				\item C++; C\#; OpenGL; Glut; GLM; GLSL; XML (XSD); Haskell; Lua; Python (Numpy, Pandas, Matplotlib, Asyncio); \LaTeX  
				\item Cisco IOS; Extreme Networking OS; Pelco Surveillance cameras; Axis Surveillance cameras; NVT Phybrige; RTSP; TCP/IP; SFPs (Copper, Single Mode Fiber, Multimode Fiber); RJ45 and RG-6 Termination
				\item Pelco VideoXpert; Avigilon Unity; Mirasys
			\end{itemize}
		\end{cvsubsection}
	\end{cvsection}
	
		\begin{cvsection}{Professional Skills}
		\begin{cvsubsection}{}{}{}	
			\begin{itemize}
				\item Excellent customer service skills, helping customers figure out the cause and solution to their issues.
				\item Computer repair, building, and maintenance.
				\item Diagnosing and resolving hardware and software issues.
				\item Experienced in teamwork and leadership roles.
				\item Experience with helping improve interdepartmental communication, working with contractors and tech support of other companies, excellent oral and written communications skills through face to face, phone, and email correspondence. 
				\item Working along side and coordinating with vendors and contractors on large project and for resolving issues and bugs.
				\item Working at height with hand and power tools.
				\item Creating clear and easy to read diagrams and documentation for systems, inventory and networks to insure fast and reliable repairs and deployment.
			\end{itemize}
		\end{cvsubsection}
	\end{cvsection}
	
\end{document}
