%% The MIT License (MIT)
%%
%% Copyright (c) 2015 Daniil Belyakov
%%
%% Permission is hereby granted, free of charge, to any person obtaining a copy
%% of this software and associated documentation files (the "Software"), to deal
%% in the Software without restriction, including without limitation the rights
%% to use, copy, modify, merge, publish, distribute, sublicense, and/or sell
%% copies of the Software, and to permit persons to whom the Software is
%% furnished to do so, subject to the following conditions:
%%
%% The above copyright notice and this permission notice shall be included in all
%% copies or substantial portions of the Software.
%%
%% THE SOFTWARE IS PROVIDED "AS IS", WITHOUT WARRANTY OF ANY KIND, EXPRESS OR
%% IMPLIED, INCLUDING BUT NOT LIMITED TO THE WARRANTIES OF MERCHANTABILITY,
%% FITNESS FOR A PARTICULAR PURPOSE AND NONINFRINGEMENT. IN NO EVENT SHALL THE
%% AUTHORS OR COPYRIGHT HOLDERS BE LIABLE FOR ANY CLAIM, DAMAGES OR OTHER
%% LIABILITY, WHETHER IN AN ACTION OF CONTRACT, TORT OR OTHERWISE, ARISING FROM,
%% OUT OF OR IN CONNECTION WITH THE SOFTWARE OR THE USE OR OTHER DEALINGS IN THE
%% SOFTWARE.

% The font could be set to Windows-specific Calibri by using the 'calibri' option

% !TeX program = lualatex

\documentclass[]{mcdowellcvcustom}

% For mathematical symbols
\usepackage{amsmath}


%for left center right alignment
\newcommand{\headerline}[3]{%
	\par\medskip\noindent
	\makebox[0pt][l]{\texttt{#1}}%
	\makebox[\textwidth][c]{#2}%
	\makebox[0pt][r]{\texttt{#3}}\par\medskip}

% Set applicant's personal data for header
\name{Nicholas Cochrane}
\address{8610 N. Cedar Ave. Apt 203 \linebreak Fresno, California}
\contacts{(559) 676-7957 \linebreak nicholascochrane.dev@gmail.com}

\begin{document}

	% Print the header
	\makeheader
	
	\headerline{linkedin.com/in/nicholas-cochrane-dev}{ }{ }
	
	% Print the content
	\begin{cvsection}{Profile}
		\vspace{2mm}
		
		Dedicated and tech-savvy college graduate with a strong passion for customer service and an extensive knowledge of computers, consumer electronics, and home appliances. Possesses excellent communication skills and a customer-centric approach, making me a valuable asset in the retail industry. Eager to leverage my technical expertise and problem-solving abilities to provide exceptional service and drive sales in a retail setting.
	\end{cvsection}
	
	\vspace{6mm}
	\begin{cvsection}{Employment\slash Experience}
		\begin{cvsubsection}{High School IT Support}{Minarets High School}{August 2014 - June 2015}			
			\begin{itemize}
				\item Volunteered working for high schools IT support team. 
				\item Computer repair, Computer imaging, Tech support
			\end{itemize}
		\end{cvsubsection}
		\vspace{2mm}
		\begin{cvsubsection}{Computer Repair and Imaging}{Minarets High School}{Summer 2015}			
			\begin{itemize}
				\item Summer Job at Minarets High School repairing and re-imaging laptops for the next school year.
			\end{itemize}
		\end{cvsubsection}

	\end{cvsection}
	
	\vspace{6mm}
	
	\begin{cvsection}{Education}
		\begin{cvsubsection}{Fresno, CA}{California State University, Fresno}{August 2015 -- May 2020}
			\begin{itemize}
				\item Graduated Spring 2020 
				\item B.S. in Computer Science. GPA: 3.90
				\item Undergraduate Coursework: Operating Systems; Databases; Big Data Analysis and Data Mining; Algorithms; Reinforcement Learning; Calculus II; Computer Graphics.
			\end{itemize}
		\end{cvsubsection}
	\end{cvsection}
	
	\vspace{6mm}
	
	\begin{cvsection}{Technical Experience}
		\begin{cvsubsection}{Projects}{}{}
			\begin{itemize}
				\item \textbf{Roguelike} (2023). Home Linux Server; Set up a personal home Linux server with a repurposed laptop for media hosting and local streaming.
				
				\item \textbf{Reversi Website} (2019). Working game site with login, online saving, reloading, AI opponents and high score Tracking.
				
				\item \textbf{Pattern Analysis for Transaction Fraud Detection} (2020). \textbf{DOI}: 10.1109/CCWC51732.2021.9376045 Data Analysis paper where our team examined the patterns of transaction fraud in large data sets. Presented at IEEE CCWC 2021.
				
			\end{itemize}
		\end{cvsubsection}
	\end{cvsection}
	
	\vspace{6mm}

	\begin{cvsection}{Skills and Knowledge}
		\begin{cvsubsection}{}{}{}	
			\begin{itemize}
				\item Experience helping customers solve technology related problems
				\item Experienced in teamwork and leadership roles
				\item Knowledgeable about computers, technology, and home appliances
				\item Critical thinking and math
				\item Adaptability and flexibility
				\item Maintains a consistently clean and organized workspace
				\item Microsoft Office Suites and Google Docs
			\end{itemize}
		\end{cvsubsection}
	\end{cvsection}
	
\end{document}
